title TBD

### 2016-01-10 SC-challenge.tex
Added a ref or two and some basic text

% Page heads
\markboth{K. Niemeyer et al.}{\emph{title TBD}}

% Title portion
\title{\emph{title TBD}}

@@

\begin{bottomstuff}
This work is supported by the National Science Foundation, under
grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.

@@

\section{Conclusions}

@@

% History dates
\received{Month 2016}{Month 2016}{Month 2016}

>>>>

% Page heads
\markboth{K. Niemeyer et al.}{title TBD}

% Title portion
\title{title TBD}

@@

\begin{bottomstuff}
This work is supported by the National Science Foundation, under ...

@@

\section{Related Work}

Ongoing efforts by the WSSSPE Software Credit Working Group and FORCE11 Software Citation Working Group

Codemeta for minimal metadata schemes in JSON and XML

transitive credit for via JSON-LD~\cite{Katz:2015aa}

\section{Challenges and Research Directions}

key challenges include
\begin{itemize}
\item standardize proper format for citing software in publications, and
\item identify necessary metadata associated with software for citation, 
\item develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem.
\end{itemize}

@@

% History dates
\received{Month Year}{Month Year}{Month Year}
